### 2016-02-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Created FDS file for DelCo East Structure and table in exp. overview report

@@

>>>>

% Load Packages
\usepackage{graphicx}
\usepackage{placeins}

@@

\begin{table}[!ht]
\small
\caption{East Structure experimental times (min:sec)}
\begin{tabular}{lcccccccccc}
 \toprule
\begin{tabular}{@{}c@{}} \textbf{Test} \\ \textbf{Number} \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{Pilot} \\ \textbf{(Ignition)} \end{tabular} & 
\multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Corner} \\ \textbf{Burner} \end{tabular}} & 
\multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Middle} \\ \textbf{Burner} \end{tabular}} & 
\multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Center} \\ \textbf{Burner} \end{tabular}} & 
\begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{West Double Door} \end{tabular} & 
\begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{East Double Door} \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{South Side} \\ \textbf{Single Door} \end{tabular} &
\begin{tabular}{@{}c@{}} \textbf{Roof Vent} \\ \textbf{Single Door} \end{tabular} 
\\
 & \textbf{On} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} &
 \textbf{Open} & \textbf{Open} & \textbf{Open}  \\
\midrule
4 & 0:00 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 7:20 & 9:20 & 10:20 \\
\bottomrule
\end{tabular}
\label{table:east_exp_times}
\end{table}
\FloatBarrier
